### 2019-07-12 manuscript/discussion.tex
shortened the final section of Discussion

\bigskip

%B: Rosana, read this carefully, please! I think it may need review:
%B: I changed nothing here, except: (1) a citealt<-citet to avoid double parentheses. (2) sp. disscussed -> discussed, (3) "If that is the case ON a system" -> "... IN a system"? (4) "hight type I errors" -> high, type I errors [comma], (5) line break in penultimate sentence.
Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as discussed in \citealt{rabosky_2010, beaulieu_2015}), but also a problem of inadequate SSE model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focal trait first used to model diversification. 
We presented a roadmap with a series of analyses that can identify whether unknown or unobservable traits are worth pursuing. 
In this roadmap, we have proposed fitting HiSSE models that have effectively shown that some binary states associated with diversification under BiSSE analyses are actually not different in net diversification terms, and instead a hidden state is linked to differences in the diversification rate \citep{beaulieu_2016}.  
If that is the case in a study system, raising the question of the identity of the hidden state should be considered as the next step in the modeling process.  % E: I would say not necessarily.  There could be other non-trait weirdnesses.  TODO: include a more comprehensive discussion of how to interpret hisse/hidden state
When considering a second candidate trait, one can model the complex interactions via a MuSSE model, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
Since MuSSE can also falsely associate traits with diversification \citep{fitzjohn_2012}, considering more heterogeneity using a hidden state model on top of the multi-state diversification model is necessary to adequately infer the effect of the complex interactions in the speciation and extinction process.
% R- new lines
Investigating the process of diversification linked to traits can be done via thorough statistical inferences that carefully evaluate multiple evolutionary histories. 
Background heterogeneity in lineage of diversification is the rule, rather than the exception. 
Inferences that question whether other complex trait interactions are hidden in this background heterogeneity are necessary because they critically contribute to the reconstruction and understanding of diversification.

>>>>

\section{Conclusion}

% E: The text previously here was great, but it read to me more like an abstract or methods/results.  I tried to make it more like a big-picture summary.  What other general points do we want to hit here?

Heterogeneity in lineage diversification across time and clades is the rule, rather than the exception.
This background heterogeneity makes it difficult to test for the association of any one, isolated trait with different rates of speciation or extinction.
Our study provides an example of how diversification linked to a particular trait can be better assessed by a suite of more inclusive models that allow for alternative explanations---whether other traits or unknown factors.
Additionally, our analysis of evolutionary pathways to polyploidy shows the importance of including diversification effects even when addressing questions that focus on trait evolution.
